\thispagestyle{fancy}
\setlength{\parindent}{18pt}

\begin{onehalfspacing}

\vspace*{40pt}

\section*{\huge Abstract}
We introduce the field of inner model theory, starting from extenders and potential premice. We prove the basic properties of mice such as comparison, the Dodd-Jensen lemma, condensation and solidity. We construct mice via the Jensen-Steel method of using robust $K^c$-constructions and then use these mice to construct the core model $K$ under the assumption that there is no proper class model with a Woodin cardinal -- this is proven without the assumption that there exists a measurable cardinal in $V$. This construction of $K$ is due to Steel and Jensen in their 2013 article ``$K$ without the measurable".

\vspace*{40pt}

\section*{\huge Preface}
We believe the reader to be well acquainted with Gödel's constructible universe $L$ (including the basic things on rudimentary functions from \cite{Jensen}), measures and ultrapowers, as well as the basic theory of forcing.

\quad Most of my notation will be standard, but as some parts of notation don't have a standard variant (yet!), some explanation is still required. I will denote the class of all ordinals by $\on$ and the direct limit of a sequence of models $\bra{\M_\alpha\mid\alpha<\theta}$ by $\colimm_\alpha\M_\alpha$. If $\pi:\M\to\N$ is $\Gamma$-preserving for some set of formulas $\Gamma$, then I'll write $\pi:\M\to_\Gamma\N$. I won't syntactically distinguish between a model and its universe, so I'll write things such as $x\in\M$ for $\M=\bra{M,\in,\hdots}$, which frees up the notation $|\M|$ for the cardinality of (the universe of) $\M$. Tuples and sequences will be written with angled brackets $\bra{x_1,\hdots,x_n}$ and (closed, open) intervals will be written with (square, round) brackets. I use $\contr$ to denote a contradiction.

\quad I would like to thank David Schrittesser for the helpful input he's given me in our discussions, and I would also thank Asger Törnquist for being the closest I've had to a mentor during my studies.

\quad \textit{Revised version update:} In this version I have fixed several errors and provided extra clarifications throughout the thesis. If you find any errors, please do let me know.

\end{onehalfspacing}
